Innovation and elaboration on the avian tree of life - supplementary materials

### 2022-10-18 Manuscript/supplementaries.tex
Update supplementaries.tex

\usepackage{hyperref}
\usepackage{lineno}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[osf]{mathpazo}
\usepackage{fullpage}
% \usepackage{float}

@@

\section{Supplementary material 1: additional results}

@@

>>>>

\usepackage{lscape}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[osf]{mathpazo}
\usepackage{fullpage}
% \usepackage{float}

@@

\begin{landscape}
\section{Supplementary material 1: glossary}

\begin{table}[ht]
\centering
\scriptsize
\begin{tabular}{p{0.2\textwidth}p{0.3\textwidth}p{0.3\textwidth}p{0.1\textwidth}p{0.1\textwidth}}
  \hline
Term in this paper         & definition in this paper & mathematical definition & in macroevolution & in microevoltion\\
  \hline
major axis of variation    & the major evolutionary ``direction'' of traits co-evolution & first eigenvector of the variance-covariance matrix  & allometry & line of genetic least resistance \\
clade                      & a monophyletic group of \textbf{species} & a subset of \textbf{shapespace} & Birds & a group of species or a population\\
species                    & the lowest evolutionary units in our analysis & a row in the \textbf{shapespace} & \textit{} & an individual\\
shapespace                 & all the possible morphological combination (observed or not) & an ordinate and orthonormal matrix & the beak shapespace & a gene space \\
novelty                    & morphological variation (either \textbf{innovation} or \textbf{elaboration}) & position of a \textbf{species} or a \textbf{clade} relative to the \textbf{major axis of variation} & & \\
elaboration                & morphological variation along the \textbf{major axis of variation} & the algebraic projection on the eigenvector & & \\
innovation                 & morphological variation away from the \textbf{major axis of variation} & the algebraic rejection from the eigenvector & & \\
variance-covariance matrix & the multidimensional relation between traits & the variation of the dimension within the \textbf{shapespace} taking into account the distance matrix between the observations (the \textbf{phylogeny} or the \textbf{clades}) & & \\
nested phylogenetic level  & the different \textbf{clades} used in this study (the whole phylogeny > super-orders > orders) & different nested \textbf{variance-covariance matrices} & & \\

\end{tabular}
\caption{Glossary of some specific terms in this manuscript}
\label{tab_glossary}
\end{table}
\end{landscape}

\section{Supplementary material 2: additional results}

@@

\begin{equation}
    \vec{a_{1}} = \frac{\vec{a} \cdot \vec{b}}{\|\sqrt{\vec{b} \cdot \vec{b}}\|}
\end{equation}
